---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tRavis
<!-- badges: start -->
![R package version](https://img.shields.io/github/r-package/v/travis-m-blimkie/tRavis/master?label=tRavis%40master)
[![R-CMD-check](https://github.com/travis-m-blimkie/tRavis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/travis-m-blimkie/tRavis/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

tRavis is a small R package which contains functions and data that are used
regularly in my day-to-day workflows. It also provides an opportunity to
practice creating, documenting, and maintaining code, within the framework of an
R package and the recommended guidelines.

## Installation
You can install tRavis from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("travis-m-blimkie/tRavis")
```

## Examples
```{r example}
library(tRavis)

# Quickly compare two lists:
tr_compare_lists(c(1, 2, 3, 4), c(3, 4, 5, 6), names = c("A", "B"))

# Create a named list of files:
tr_get_files(
  directory = system.file("extdata", package = "tRavis"),
  pattern = "test",
  date = TRUE,
  remove_string = "test_"
)

# Neatly truncate strings:
tr_trunc_neatly(
  x = "This is a long string that we want to break neatly",
  l = 40
)
```

More details and examples can be found at the GitHub Pages website: 
<https://travis-m-blimkie.github.io/tRavis/>

## Authors
Travis Blimkie is the originator and principal contributor. You can check the
list of all contributors
[here](https://github.com/travis-m-blimkie/tRavis/graphs/contributors).

## License
This project is written under the MIT license, available
[here.](https://github.com/travis-m-blimkie/tRavis/blob/master/LICENSE.md)

## Acknowledgements
Thanks to everyone in the lab who has used these functions and provided
ideas/feedback!
